---
title: "Network-in-R"
author: "Nima Niarad"
date: "7/13/2021"
output: rmarkdown::github_document
---

<style> body {text-align: justify} </style> <!-- Justify text. -->


**Making a Network in R 

Sometimes there is a huge network of people in a company. Not just limited to the company itself but also includes people outside the company. 

You want to find out their connections and know most important persons. For example, consider a non-profit company that want to know how their connections can help them to raise more fund. 

We can do this in R. 

1 - Loading Library...

```{r setup, echo=FALSE}
library(dplyr)
library(igraph)
```

2 - Loading the Data...

```{r}
BCTA <- read.csv("C:/Nima/Rstudio/Git/Data/BCTA.csv", header=T, as.is=T)
```

3 - First making symmetric matrix:
```{r}
d <-BCTA %>%
  dplyr::count(Board,Chamber) %>%
  tidyr::spread(key = Board,value = n)
d[is.na(d)] = 0
mtx <-as.matrix(d)
```

As we see in the environment, it is symmetrical. 

4 - Let's Making a network and plot it: 

```{r, warning=FALSE}
ntwork <-graph.adjacency(mtx, mode="undirected", diag=FALSE, weighted=TRUE)

plot(ntwork, vertex.label.color = "black", layout = layout_in_circle(ntwork))
```

It is a nice clean graph but it cannot help us to understand who is more central to the network. 

Mike has more connections than the others but it should not be the whole story!

```{r}
plot(ntwork, layout = layout.random, vertex.label.cex=c(0.4), vertex.color=degree(ntwork)*25)
```

Now lets's do some analysis:

```{r}
df <- data.frame(deg = degree(ntwork),cls = closeness(ntwork), btw = betweenness(ntwork))
df %>%
  arrange(desc(btw))
```

Node Mike has the highest degree of centrality. It is connected to three other nodes in the network, more than any other node.

However, closeness and betweenness are telling a different story. The first two on the top have 2 degrees! It is proved we cannot decide the centrality just by degree. Let's see the betweenness separately to find out

who the persons are:

If we look at just betweenness, we can find out who has the highest betweenness:


```{r}
betweenness(ntwork)
```

Arnold and Fred are the nodes that control the flow of information in the network. 

This is the path that most other ones have to go through these two to reach other ones. So, those are our guys! 


